{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
added def

	\begin{equation}\label{HSKernal}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
	\end{equation}

	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda^{m}$ for all $m$ since it is a positive compact self-adjoint operator (cf. \cite{alexanderian_KLexpansion_2015}). Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index. Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g. $Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m < n$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. The proofs are provided at \ref{Proof1} and \ref{Proof2}.

@@

	\section{Proofs}

	\cite{alexanderian_KLexpansion_2015} was referred for the following proofs.

>>>>

	\begin{equation}\label{HSKernal}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
	\end{equation}
	More exact definitions are provided at \ref{def_HS}. Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda^{m}$ for all $m$ since it is a positive compact self-adjoint operator (cf. \cite{alexanderian_KLexpansion_2015}). Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index. Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g. $Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m < n$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. The proofs are provided at \ref{Proof1} and \ref{Proof2}.

@@

	\section{Definition and Proofs}
	\cite{alexanderian_KLexpansion_2015} was referred for the following definitions and proofs.

	\subsection{Definition (Hilbert-Schmidt Operator)}\label{def_HS}
	Given a bounded domain $\mathcal{A} \subset \mathbb{R}^n$, we call a function $c : \mathcal{A} \times \mathcal{A} \rightarrow \mathbb{R}$ a Hilbert-Schmidt kernel if
	\begin{equation}
		\int_{\mathcal{A}} \int_{\mathcal{A}} \vert c(x,y) \vert ^2 dx dy < \infty
	\end{equation}
	where $c \in \mathbb{L}^2(\mathcal{A} \times \mathcal{A})$. Let $K$ be an integral operator on $\mathbb{L}^2(\mathcal{A})$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^2(\mathcal{A})$, by

	\begin{equation}
		[K\nu](x) = \int_{\mathcal{A}} c(x,y) \nu(y) dy
	\end{equation}
	When an integral operator $K$ is linear and bounded, it is called a Hilbert-Schmidt operator. The linearity of the operator $K$ is simply proved. Additionaly assume that $\alpha, \beta \in \mathbb{R}$ and $\theta \in \mathbb{L}^2(\mathcal{A})$.
	\begin{equation}
		\begin{split}
			[K (\alpha \nu + \beta \theta)](x) =& \int_{\mathcal{A}} c(x,y)(\alpha \nu(y) + \beta \theta(y)) dy\\
			= & \int_{\mathcal{A}} c(x,y) \alpha \nu(y) dy + \int_{\mathcal{A}} c(x,y) \beta \theta(y) dy\\
			= & \alpha\int_{\mathcal{A}} c(x,y) \nu (y) dy + \beta\int_{\mathcal{A}} c(x,y) \theta (y) dy\\
			= & \alpha[K\nu](x) + \beta[K\theta](x)
		\end{split}
	\end{equation}
	For boundedness of the oprator $K$,
	\begin{equation}
		\begin{split}
			\Vert K\nu \Vert^{2}_{\mathbb{L}^2(\mathcal{A})} = & \int_{\mathcal{A}} \biggl\vert [K\nu](x) \biggr\vert^2 dx\\
			= &\int_{\mathcal{A}} \biggl\vert \int_{\mathcal{A}}c(x,y)\nu(y)dy \biggr\vert^2dx\\
			\leq & \int_{\mathcal{A}}\biggl(\int_{\mathcal{A}}\vert c(x,y) \vert^2dy\biggr) \biggl(\int_{\mathcal{A}}\vert \nu(y) \vert ^2 dy \biggr)dx \quad \text{(Cauchy-Schwarz)}\\
			= & \Vert c \Vert_{\mathbb{L}^2(\mathcal{A} \times \mathcal{A})}\Vert \nu \Vert_{\mathbb{L}^2} < \infty
		\end{split}
	\end{equation}
